Practical Considerations for Lomb-Scargle Periodic Analysis

### 2016-12-13 paper.tex
Add Nyquist discussion

\subsection{Effect of a Dirac Comb}
Another window function that commonly arises is when a continuous signal is
sampled instantaneously at regular intervals.
Such an observation is, in effect, a point-wise product between the true
underlying signal and a Dirac comb with the $T$ parameter matching the spacing
of the observations; this is illustrated in \fig{comb_window_1}.

@@

Interestingly, because the Fourier transform of a Dirac comb is another Dirac
comb, the effect of such an observing window is to create a long sequence
of aliases with a spacing of $1/T$.
With this in mind, we can be assured that evaluating the transform in the
range $[-(2T)^{-1}, (2T)^{-1}]$ is sufficient to capture all the relevant
frequency information: everything else will simply be an alias of what appears
within that range.

>>>>

\subsection{The Dirac Comb and the Nyquist Limit}
Another window function that commonly arises is when a continuous signal is
sampled instantaneously at regular intervals.
Such an observation is, in effect, a point-wise product between the true
underlying signal and a Dirac comb with the $T$ parameter matching the spacing
of the observations; this is illustrated in \fig{comb_window_1}.

@@

Interestingly, because the Fourier transform of a Dirac comb is another Dirac
comb, the effect of such an observing window is to create a long sequence
of aliases with a spacing of $1/T$.
With this in mind, we can be assured in this case that evaluating the
transform in the range $-(2T)^{-1} \le f < (2T)^{-1}$ is sufficient to capture
all the relevant frequency information: the signal outside that range is a
string of duplicates of what lies in that range.

The example in \fig{comb_window_1} is somewhat of a best-case scenario, because
the true Fourier transform lies entirely in the range noted above.
If we change the sampling rate so that this is no longer the case, we will
have a situation similar to that in \fig{comb_window_2}.
With a lower sampling rate, the signal transform no longer fits within the
frequency window, and the true Fourier transform {\it cannot be recovered}
from the observed transform.

This implies that if we have a regularly-sampled function with a sampling
rate of of $f_0 = 1/T$, we can only fully recover the freuqency information
if the signal is {\it band-limited} between frequencies $\pm f_0/2$.
This is one way to motivate the famous Nyquist sampling limit, which says
that to fully represent the frequency content of a ``band-limited signal''
with all Fourier power in the range $\pm B$, we must sample the data with a
rate of at least $2B$.
